---
title: "collectivism score calculation"
output: html_document
date: "2024-03-11"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Voting Data
```{r, echo=FALSE}
libertarian <- read.csv("/Users/erin/Desktop/statecollectivism_score/libertarian/libertrarian_election.csv")

library(dplyr)
libertarian <- libertarian %>% 
  select(year, state, percentage)

library(stringr)
libertarian$state <- str_to_title(tolower(libertarian$state))
head(libertarian)

library(tidyr)
libertarian_formatted <- libertarian %>%
  pivot_wider(names_from = year, values_from = percentage) %>% 
  mutate(state = ifelse(state == "District Of Columbia", "District of Columbia", state))

libertarian_clean <- libertarian_formatted %>% 
  mutate(libertarian_vote = rowMeans(select(., c("2008", "2012", "2016", "2020"))))
head(libertarian_clean)

write.csv(libertarian_clean, "/Users/erin/Desktop/statecollectivism_score/libertarian/libertarian_clean.csv")

libertarian_short <- libertarian_clean %>% 
  select(state, libertarian_vote)
  
```

#American Community Survey
```{r, echo=FALSE}
ACS <- read.csv("/Users/erin/Desktop/statecollectivism_score/American Community Survey 5-year/ACS22_5year.csv")
head(ACS)

```

#Religious Affiliation
```{r, echo=FALSE}
religion <- read.csv("/Users/erin/Desktop/statecollectivism_score/religion/Adherents_rate.csv")
head(religion)

religion <- religion %>% 
  mutate(state = ifelse(state == "District Of Columbia", "District of Columbia", state)) %>% 
  rename("religious_adherents" = "adherents_rate")


```

#Combine
```{r, echo=FALSE}
mergedata <- merge(ACS, libertarian_short, by = "state")
mergefinal <- merge(mergedata, religion, by = "state")

#write.csv(mergefinal, "state_index.csv")

```



#Scaling and Standardization
Reverse coded items:
1. people living alone
2. elders living alone
3. divorce to marriage ratio
4. vote for libertarian
5. self-employed

notes: living with grandchildren, religion affiliation, and carpooling are not reverse coded

After reverse coding, these items are summed as an overall collectivism score. I linear transformed the collectivism score, so that the score is from 0 to 100. The standardized alpha is 0.63.

```{r, echo=FALSE}
#mergefinal <- read.csv("state_index.csv")

colnames(mergefinal)

#people living alone
mergefinal$living_alone_reverse <- 1 - mergefinal$living_alone
#elders living alone
mergefinal$living_alone_65over_reverse <- 1 - mergefinal$living_alone_65over
#living with grandchildren - not reversed
#divorce to marriage ratio
mergefinal$divorce_marriage_reverse <- 1 / mergefinal$divorce_marriage
#religion affiliation - not reversed
#vote for libertarian
mergefinal$libertarian_vote_reverse <- 1 - mergefinal$libertarian_vote
#carpooling - not reversed
#self-employed
mergefinal$self_employed_reverse <- 1 - mergefinal$self_employed

mergefinal_short <- mergefinal %>% 
  select(state, living_alone_reverse, living_alone_65over_reverse, living_grandchildren, 
         divorce_marriage_reverse, religious_adherents, libertarian_vote_reverse,
         carpooling, self_employed_reverse) 

data_cleaned <- mergefinal_short %>% 
  mutate_at(vars(2:9), scale) %>% 
  rename_with(~ paste0(., "_z"), 2:9) %>%
  mutate(state_collectivism_raw = rowSums(select(., 2:9))) 

#linear transformation to scale the scores from 0 to 100
score_range <- range(data_cleaned$state_collectivism_raw)
data_cleaned$state_collectivism_score <- ((data_cleaned$state_collectivism_raw - score_range[1]) / (score_range[2] - score_range[1])) * 100

data_scoreonly <- data_cleaned %>% 
  select(state,state_collectivism_raw, state_collectivism_score)

data_all <- merge(mergefinal, data_scoreonly, by = "state")

#write.csv(data_all, "state_collectivism_score.csv")


```


#Descriptives
```{r, echo=FALSE}
#collectivism score distribution
hist(data_all$state_collectivism_score,
     main = "State Collectivism Score Distribution",
     xlab = "Collectivism Score",
     ylim = c(0, 25), 
     xlim = c(0, 100))


#Cronbach's alpha: standardized alpha = 0.61
library(psych)

alpha <- alpha(data_all[, c("living_alone_reverse", "living_alone_65over_reverse", 
                            "living_grandchildren", "divorce_marriage_reverse",
                            "religious_adherents", "libertarian_vote_reverse", 
                            "carpooling", "self_employed_reverse")], 
               keys = c(1, 1, 1, 1, 1, 1, 1, 1))
alpha


#correlation matrix
corrdata <- data_all %>% 
    select(2:9, 15) %>% 
    rename("living alone" = "living_alone",
           "elderly people living alone" = "living_alone_65over",
           "living with grandchildren" = "living_grandchildren",
           "divorce to marriage ratio" = "divorce_marriage",
           "with religious affiliation" = "religious_adherents",
           "voting Libertarian" = "libertarian_vote",
           "carpooling to work" = "carpooling",
           "self-employed workers" = "self_employed",
           "state collectivism score" = "state_collectivism_score")
  
library(Hmisc)
res2 <- rcorr(as.matrix(corrdata))
res2
  
res2$P[is.na(res2$P)] <- 1
  
library(corrplot)
corrplot(res2$r, type="upper", order="hclust", method="color",
           p.mat = res2$P, sig.level = 0.05, insig = "pch", pch.cex = 2, pch = 4,
           addCoef.col = "black", number.cex = 0.6,
           tl.col = "black",tl.srt = 45,tl.cex = 0.8, 
           diag = FALSE)


```


#Comparison to v-c score (1994)
```{r, echo=FALSE}
cov_url <- "https://raw.githubusercontent.com/QinggangYu/SURVMETH727_final_project/main/Predictors_US_states.csv"
cov <- read.csv(url(cov_url))

cov <- cov %>% 
  select("State", "Collectivism") %>% 
  rename("state" = "State",
         "VC_score" = "Collectivism")

comparedata <- merge(data_scoreonly, cov, by = "state")

comparedata <- comparedata %>%
  mutate(rank_new = rank(desc(state_collectivism_score), ties.method = "min")) %>% 
  mutate(rank_old = rank(desc(VC_score), ties.method = "min"))

#linear transformation to scale the scores from 0 to 100
score_range <- range(comparedata$VC_score)
comparedata$VC_score_t <- ((comparedata$VC_score - score_range[1]) / (score_range[2] - score_range[1])) * 100

mean(comparedata$VC_score_t)
mean(comparedata$state_collectivism_score)

cor.test(comparedata$state_collectivism_score, comparedata$VC_score_t)
cor.test(comparedata$state_collectivism_score, comparedata$VC_score)
cor.test(comparedata$rank_new, comparedata$rank_old)



```